Who was most affected by COVID-19 in Toronto

### 2022-02-07 outputs/paper/paper.Rmd
done

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(palmerpenguins)
library(kableExtra)
wd <- getwd()
wd
setwd("../..")
covid19_cases_cleaned <- read_csv("inputs/data/COVID19-cases-clean.csv")
```

@@

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(palmerpenguins)
library(kableExtra)
wd <- getwd()
wd
setwd("../..")
covid19_cases_cleaned <- read_csv("inputs/data/COVID19-cases-clean.csv")
head(covid19_cases_cleaned)
```

@@

## Conclusion
Our findings clearly revealed that COVID-19 hits certain people and neighborhood really hard and they require more attention from the government. Luckily, the City of Toronto is aware of this situation and have launched support programs
targeting those neighborhood. For instance, the City of Toronto is offering free self-isolation sites for those people diagnosed with COVID-19 and is also giving seniors and people with underlying health condition top priority in the vaccination program.
